\Large \bf Dismal Code: Studying the Evolution of Security Bugs

### 2013-10-08 docs/evol.tex
changed image captions, removed page numbers
minor fixes

\maketitle
\thispagestyle{empty}

@@

In this paper we present how we used a large software ecosystem to analyse the
relationship of different types of security vulnerabilities to 
evolving software packages.
For our research we used {\it FindBugs},\endnote{\url{http://findbugs.sourceforge.net/}}
a static analysis tool that examines bytecode to detect software bugs and has already been used in
research~\cite{AP10,HP07,SHP06}.
Specifically, we ran FindBugs on all the project
versions of all the projects that exist in the
{\it Maven Central Repository}\endnote{\url{http://mvnrepository.com/}}
(approximately 265GB of data---see Section~\ref{sec:data}).
Then we observed the changes that involved the security bugs and their characteristics.
%This research builds upon our earlier work on the topic~\cite{MGS12}.

@@

Maven is a build automation tool used primarily for Java projects and it is
hosted by the Apache Software Foundation.
It uses {\sc xml} to describe the software project being built, its dependencies
on other external modules, the build order, and required plug-ins.

@@

\begin{table}[t]
\centering
\caption{Descriptive Statistics Measurements for the Maven Repository}
\label{tbl:repository}
\begin{tabular}{l r}
\hline
Measurement & Value\\
 \hline
Projects & 17,505\\
Versions (total) & 115,214\\
Min (versions per project) & 1\\
Max (versions per project) & 338\\
Mean (versions per project) & 6.58\\
Median (versions per project) & 3\\
Range (over versions) & 337\\
1$^{st}$ Quartile (over versions) & 1\\
3$^{rd}$ Quartile (over versions) & 8\\
\hline
\end{tabular}
\end{table}

@@

\begin{table*}[t]
\centering
\caption{Bug Categorisation According to FindBugs}
\label{tbl:bug-cat}
\begin{tabular}{l p{29em}}
\hline
Category & Description\\
\hline
Bad Practice & Violations of recommended and essential
coding practice. \\
Correctness & Involves coding misting a way that is particularly different from the other bug sakes resulting in code
that was probably not what the developer intended. \\
Experimental & Includes unsatisfied obligations. For instance,
forgetting to close a file. \\
Internationalization (i18n) & Indicates the use of non-localized methods. \\
Multi-Threaded ({\sc mt}) Correctness & Thread synchronization issues. \\
Performance & Involves inefficient memory usage allocation, usage 
of non-static classes. \\
Style & Code that is confusing, or
written in a way that leads to errors.\\
Malicious Code & Involves variables or fields exposed to classes that should
not be using them. \\
Security & Involves input validation issues, unauthorized database connections
and others. \\
\hline
\end{tabular}
\end{table*}

@@

\begin{table*}[t]
\centering
\caption{Number of Project Releases that Contain at Least One ``Security
  High" Bug}
\label{tbl:sev}
\leavevmode
	\begin{tabular}{p{31em} r}
	\hline
	Bug Description & Number of Project Releases\\
 	\hline
	{\sc hrs}: {\sc http} cookie formed from untrusted input & 151\\
	{\sc hrs}: {\sc http} response splitting vulnerability & 1,579\\
	{\sc pt}: absolute path traversal in servlet  & 103\\
	{\sc pt}: relative path traversal in servlet & 57\\
	{\sc sql}: non-constant string passed to execute method on an {\sc sql} statement & 1,875\\
	{\sc sql}: a prepared statement is generated from a non-constant String & 1,486\\
	{\sc xss}: {\sc jsp} reflected cross site scripting vulnerability & 18\\
	{\sc xss}: Servlet reflected cross site scripting vulnerability in error page & 90\\
	{\sc xss}: Servlet reflected cross site scripting vulnerability & 142\\
	\hline
	\end{tabular}
\end{table*}

@@

>>>>

\maketitle
%\thispagestyle{empty}
\thispagestyle{empty}
\pagestyle{empty}

@@

In this paper we present how we used a large software ecosystem to analyse the
relationship of different types of security vulnerabilities to 
evolving software packages.
For our research we used {\it FindBugs},\endnote{\url{http://findbugs.sourceforge.net/}}
a static analysis tool that examines bytecode to detect software bugs and has already been used in
research~\cite{AP10,HP07,SHP06}.
Specifically, we ran FindBugs on all the project
versions of all the projects that exist in the
{\it Maven Central Repository}\endnote{\url{http://mvnrepository.com/}}
(approximately 265{\sc gb} of data---see Section~\ref{sec:data}).
Then we observed the changes that involved the security bugs and their characteristics.
%This research builds upon our earlier work on the topic~\cite{MGS12}.

@@

Maven is a build automation tool used primarily for Java projects and it is
hosted by the Apache Software Foundation.
It uses {\sc xml} to describe the software project being built, its dependencies
on other external modules, the build order, and required plug-ins.
To build a software component, it dynamically downloads Java libraries
and Maven plug-ins from the Maven central repository,
and stores them in a local cache. The repository can be updated with
new projects and also with new versions of existing projects.

@@

\begin{table}[t]
\centering
\label{tbl:repository}
\begin{tabular}{l r}
\hline
Measurement & Value\\
 \hline
Projects & 17,505\\
Versions (total) & 115,214\\
Min (versions per project) & 1\\
Max (versions per project) & 338\\
Mean (versions per project) & 6.58\\
Median (versions per project) & 3\\
Range (over versions) & 337\\
1$^{st}$ Quartile (over versions) & 1\\
3$^{rd}$ Quartile (over versions) & 8\\
\hline
\end{tabular}
\caption{Descriptive Statistics Measurements for the Maven Repository}
\end{table}

@@

\begin{table*}[t]
\centering
\label{tbl:bug-cat}
\begin{tabular}{l p{29em}}
\hline
Category & Description\\
\hline
Bad Practice & Violations of recommended and essential
coding practice. \\
Correctness & Involves coding misting a way that is particularly different from the other bug sakes resulting in code
that was probably not what the developer intended. \\
Experimental & Includes unsatisfied obligations. For instance,
forgetting to close a file. \\
Internationalization (i18n) & Indicates the use of non-localized methods. \\
Multi-Threaded ({\sc mt}) Correctness & Thread synchronization issues. \\
Performance & Involves inefficient memory usage allocation, usage 
of non-static classes. \\
Style & Code that is confusing, or
written in a way that leads to errors.\\
Malicious Code & Involves variables or fields exposed to classes that should
not be using them. \\
Security & Involves input validation issues, unauthorized database connections
and others. \\
\hline
\end{tabular}
\caption{Bug Categorisation According to FindBugs}
\end{table*}

@@

\begin{table*}[t]
\centering
\label{tbl:sev}
\leavevmode
	\begin{tabular}{p{31em} r}
	\hline
	Bug Description & Number of Project Releases\\
 	\hline
	{\sc hrs}: {\sc http} cookie formed from untrusted input & 151\\
	{\sc hrs}: {\sc http} response splitting vulnerability & 1,579\\
	{\sc pt}: absolute path traversal in servlet  & 103\\
	{\sc pt}: relative path traversal in servlet & 57\\
	{\sc sql}: non-constant string passed to execute method on an {\sc sql} statement & 1,875\\
	{\sc sql}: a prepared statement is generated from a non-constant String & 1,486\\
	{\sc xss}: {\sc jsp} reflected cross site scripting vulnerability & 18\\
	{\sc xss}: Servlet reflected cross site scripting vulnerability in error page & 90\\
	{\sc xss}: Servlet reflected cross site scripting vulnerability & 142\\
	\hline
	\end{tabular}
\caption{Number of Project Releases that Contain at Least One ``Security
  High" Bug}
\end{table*}

@@

\theendnotes
